RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

>>>>

Correlation between cell types
```{r corr.celltype}
C = get_pairwise_sharing( resMash )

corrplot( C, addCoef.col = "black", title = "Pairwise sharing",
  col=colorRampPalette(c("blue","white","red"))(200),  cl.lim=c(-1,1) )
```

```{r r heterogeneity}
library(metafor)
library(qqman)

df_het = mclapply( 1:nrow(B.hat), function(j){

  fit = rma( B.hat[j,], sei = se.hat[j,])

  data.frame( EnsID = rownames(B.hat)[j], 
    Isq = fit$I2, 
    Hsq = fit$H2, 
    p.het = fit$QEp)
  },mc.cores = 12)
df_het = do.call(rbind, df_het)

# resMash$result$PosteriorMean[j,]

par(mfrow=c(1,2))
hist(df_het$p.het)
qq(df_het$p.het)

nDE = sum(p.adjust(df_het$p.het, "fdr") < 0.05)
pi1 = 1 - qvalue(df_het$p.het)$pi0

# Gene set analysis of heterogeneity
stat = qchisq(df_het$p.het, 1, lower.tail=FALSE)
names(stat) = df_het$EnsID

geneSets_GO = get_GeneOntology()
geneSets = recodeToList(geneSets_GO)

index = ids2indices(geneSets, names(stat))
index = index[sapply(index, length) >= 15]
index = index[sapply(index, length) < 500]

res_het = cameraPR( stat, index, use.ranks=TRUE)

res_het[res_het$FDR < 0.05] %>% kable() %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

Number of DE genes: `r nDE`. pi1 = `r pi1`
